---
title: ""
author: "Binod Jung Bogati"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(broom)
library(knitr)
```


After a great discussion started by Jesse Maegan (@kiersi) on Twitter, I decided to post a workthrough of some (fake) experimental treatment data. These data correspond to a new (fake) research drug called AD-x37, a theoretical drug that has been shown to have beneficial outcomes on cognitive decline in mouse models of Alzheimer’s disease. In the current experiment we will be statistically testing whether the drug was effective in reducing cognitive impairment in dementia patients. See the data HERE.

We will be using MMSE (mini-mental status exam) scores to assess the degree of cognitive impairment. In a real clinical trial, many other variables would be recorded, but for the sake of a straightforward but multi-variate example we will stick to just MMSE.


```{r}
library(tidyverse)
```



```{r}
library(readxl)

# read excel file
raw_df <- read_xlsx("./data/ad_treatment.xlsx")


```


```{r}
glimpse(raw_df)
```
## Age 

```{r}
raw_df %>% 
 summarise(min = min(age), max = max(age))
```
## Age distribution

```{r}
g2 <- ggplot(raw_df, aes(x = age)) +
  geom_density(fill = "blue")
g2
```

```{r}
# raw_df <- raw_df %>% 
#   mutate(sex = if_else(sex == 0, "Female", "Male"))
```


```{r}
# raw_df %>% 
#   select(drug_treatment , health_status) %>% 
#   table()


raw_df %>% 
  count(drug_treatment, health_status) 
```
## Missing Value

```{r}
raw_df %>% 
  summarize(na_count = sum(is.na(mmse)))
```

```{r}
table(raw_df$drug_treatment, raw_df$health_status)
```
```{r}
table(raw_df$drug_treatment, raw_df$health_status, raw_df$sex)
```
Alternate, way

```{r}
raw_df %>% 
  count(drug_treatment, health_status, sex)
```


## Data exploration of dependent variable

Before running our summary statistics we can actually visualize the range, central tendency and quartiles via a geom_boxplot call.

```{r}

ggplot(data = raw_df, # add the data
       aes(x = drug_treatment, y = mmse, # set x, y coordinates
           color = drug_treatment)) +    # color by treatment
  geom_boxplot() +
  facet_grid(~health_status) + # create panes base on health status
  coord_flip()

```
### Summary

```{r}
raw_df %>% 
  glimpse()
```


## Factorize

```{r}
sum_df <- raw_df %>% 
            mutate(
              sex = factor(sex, 
                  labels = c("Male", "Female")),
              drug_treatment =  factor(drug_treatment, 
                  levels = c("Placebo", "Low dose", "High Dose")),
              health_status = factor(health_status, 
                  levels = c("Healthy", "Alzheimer's"))
              )
```

## Calculate

```{r}
sum_df <- sum_df %>%   
  group_by(sex, health_status, drug_treatment) %>%  
  summarize(mmse_mean = mean(mmse),   
            mmse_se = sd(mmse)/sqrt(n()),
            n_samples = n()) %>%
  ungroup() # ungrouping variable is a good habit to prevent errors


sum_df
```

## Save the file to disk

```{r}
write_csv(sum_df, "adx37_sum_stats.csv")



```

## Plotting summary statistics

```{r}
g <- ggplot(data = sum_df, # add the data
       aes(x = drug_treatment,  #set x, y coordinates
           y = mmse_mean,
           group = drug_treatment,  # group by treatment
           color = drug_treatment)) +    # color by treatment
  geom_point(size = 3) + # set size of the dots
  facet_grid(sex~health_status) # create facets by sex and status
g

```


## Statistics

```{r}
# set up the statistics df
stats_df <- raw_df %>% # start with data
   mutate(drug_treatment = factor(drug_treatment, levels = c("Placebo", "Low dose", "High Dose")),
         sex = factor(sex, labels = c("Male", "Female")),
         health_status = factor(health_status, levels = c("Healthy", "Alzheimer's")))

glimpse(stats_df)
```

```{r}
glimpse(sum_df)
```


### ANOVA

```{r eval=F}
# pseudocode example of ANOVA call

aov(dependent_variable ~ independent variable, data = data_df)
```

```{r}
# this gives main effects AND interactions
ad_aov <- aov(mmse ~ sex * drug_treatment * health_status, 
        data = stats_df)


ad_aov
```


```{r}
# this would give ONLY main effects
ad_aov <- aov(mmse ~ sex + drug_treatment + health_status, data = stats_df)

ad_aov
```

```{r}
# look at effects and interactions
summary(ad_aov)


ad_aov
```

```{r}
# this extracts ANOVA output into a nice tidy dataframe
tidy_ad_aov <- tidy(ad_aov)

# which we can save to Excel
write_csv(tidy_ad_aov, "ad_aov.csv")
```


```{r}
# pairwise t.tests
ad_pairwise <- pairwise.t.test(stats_df$mmse,
                               stats_df$sex:stats_df$drug_treatment:stats_df$health_status, 
                               p.adj = "none")
```

```{r}
# look at the posthoc p.values in a tidy dataframe
head(tidy(ad_pairwise))
```

```{r}
# tidy
tidy_ad_pairwise <- tidy(ad_pairwise)

# save to excel
write_csv(tidy_ad_pairwise, "tidy_ad_pairwise.csv")
```

```{r}
# call and tidy the tukey posthoc
tidy(
                      TukeyHSD(ad_aov, 
                              which = 'sex:drug_treatment:health_status')
                      )



TukeyHSD(ad_aov)

tidy(TukeyHSD(ad_aov, 'male:drug_treatment:health_status'))

??TuckeyHSD

summary(ad_aov)

# save to excel
write_csv(tidy_ad_tukey, "tukey_ad.csv")

head(tidy_ad_tukey)
```

























