---
title: "advanced_data_viz_participants"
author: "SanjayHamal"
date: "9/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
food<- read_csv("./data/kalimati.csv")

expensive_food_2021<- food %>% filter(Date>=as.Date("2021-01-01")) %>% group_by(Commodity, Unit) %>% summarise(Mean_price= mean(Average)) %>% arrange(desc(Mean_price)) %>% head(n=15)

Lowest_priced_food<- food %>% mutate(Year=lubridate::year(Date), Unit=tolower(Unit)) %>%filter(Unit == "kg") %>%  group_by(Year) %>% filter(Average== min(Average)) %>%select(-Date, -SN) %>%  distinct()

tomato_price<- food %>% mutate(Year=lubridate::year(Date)) %>% filter(Commodity=="Tomato Big(Nepali)") %>% group_by(Year, Commodity, Unit) %>%  summarise(Average_price= mean(Average))


vegetable_price<-food %>% mutate(Year=lubridate::year(Date)) %>% filter(Commodity %in% c("Tomato Big(Nepali)", "Potato White", "Onion Dry (Indian)")) %>% group_by(Year, Commodity, Unit) %>%  summarise(Average_price= mean(Average))

```

# Task 1:
# -Observe Kalimati bazar's food dataset:

```{r}
food
```

# Task 2
# - From above dataset, we have summarised top 15 highest priced food items of 2021 for you.
# - Observe the "expensive_food_2021" dataset.


```{r}
expensive_food_2021

```

# Task 3
#- Observe the unsorted scatter graph : Commodity vs Mean_price

```{r}

ggplot(data = expensive_food_2021)+
  geom_point(mapping = aes(x=Mean_price, y= Commodity))

```
#Task 4:
# -Sort the Commodity from lowest Mean_price to Highest Mean_price in graph:


```{r}
# Hint: fct_reorder(value_to_reorder, reorder_by) helps to reorder values in graph. 

ggplot(data = expensive_food_2021)+
  geom_point(mapping = aes(x=Mean_price,    y=  fct_reorder(Commodity    ,   Mean_price)       )) +        #fill the missing values in y.
  
  labs(x="Mean price(per KG)", y = "Commodity")
```
# Task5[Homework]
# -Reorder the Commodity values such that "Gundruk" and "Chilli Dry" appear first at the bottom of y-axis in the graph: 

```{r}
#Hint: fct_relevel(column name, values)


ggplot(data = expensive_food_2021)+
  geom_point(mapping = aes(x=Mean_price,    y=  fct_relevel(Commodity    ,  c("Gundruk", "Chilli Dry")  ))) +        #fill the missing values in y.
  
  labs(x="Mean price(per KG)", y = "Commodity")

```
# Task 6:
# - We have filterd out the lowest priced food items in each year from 2013-2021->"Lowest_priced_food"
# - Sort the bar graph in descending order



```{r}

#Hint: column_name %>% fct_infreq() orders in descending order


Lowest_priced_food

graph1<-ggplot(data = Lowest_priced_food)+
  geom_bar(mapping= aes(x= Commodity %>% fct_infreq(), fill= Commodity))+
  
  labs(title = "Count of lowest priced food",
       subtitle = "[2013-2021]",
       x= "Commodity")
  
graph1  
```
#Task 7
#  Fill the colors manually: c("Red", "Green", "Blue", "Yellow")

```{r}
#Hint: scale_fill_manual(values= ____)

graph1+scale_fill_manual(values =  c("Red", "Green", "Blue", "Yellow")   )

```

# Task 8
# Here, we have a bar chart with proportion.
# Convert the y-axis scales to percent.
# Give breaks: 0, 0.25, 0.50

```{r}
#Hint: Use scale_y_continuous and scales::percent 
ggplot(data = Lowest_priced_food)+
  geom_bar(mapping= aes(x= Commodity, y=..prop.., group=1))+
  
  labs(title = "Percent of lowest priced food",
       subtitle = "[2013-2021]",
       x= "Commodity", y= "Percent")+
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.25, 0.50))
  

```

#Task9 [Homework]
# Give breaks: 2013,2015, 2017, 2019, 2021 to x_axis:
# Increase the lower limit of Y-axis to 5 and upper limit to 80
# Put Rs as a prefix in Y axis.



```{r}
graph2<-ggplot(data = vegetable_price,mapping = aes(x=Year, y=Average_price, color= Commodity))+geom_line()+
  labs(title = "Average price of Vegetables",
       subtitle = "[Between 2013-2021]",
       x="Year",
       y= "Annual Average price",
       caption="Source: Opendata Nepal")+
  
  scale_x_continuous(
    breaks = c(2013,2015, 2017, 2019, 2021)
  )+
  
  scale_y_continuous(
    limits = c(5,80),
    labels = function(x){paste0("Rs ", x)}
  )
graph2
```

#Task 10
#  In graph2,Reverse the order of legends
#  Distribute legend values in 2 rows rather than one in each row.

```{r}
graph2+
  guides(color=guide_legend(reverse = T, nrow = 2 ,  byrow = T))

```
#Task 13
# Shift the legend's position to the bottom for graph1 with a spacing of 0.5 cm.
# Remove legend title.
#Remove legend title and adjust text size of legend to 12


```{r}
graph2+
  theme(legend.position = "bottom",
        legend.spacing.x = unit(0.5, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 12))

```
#Task14[Assignment]
# Remove legends from graph1

```{r}
graph1+
  theme(legend.position = "none")
```

```{r fig.showtext = TRUE}
library(extrafont)
library(extrafontdb)
#font_import()
loadfonts(device = "win")
library(showtext)
showtext_auto()
graph2+
  theme(axis.text = element_text(
    
    family = "sans"
  ))


```

# Task 15
# Change the axis title's font to 'sans' and color to 'gray' for graph2

```{r}

graph2+
  theme(axis.title = element_text(
    
    family = "sans",
    colour = "gray"
    
  ))
```
# Task 16
# For graph 2:
# Change the x-axis label color to 'gray' and rotate it by   45 degree.
# Change the y-axis label color to 'gray' and face to        italic.

```{r}
graph2+
  theme(
    axis.text.x = element_text(colour = "gray", angle = 45),
    axis.text.y = element_text(color = "gray", face = "italic")
  
  
  
  )
```
# Task 17
# The axis ticks are pointhing outwards in graph2.
# Change the axis ticks such that they are pointing inwards.
# Also, change the color of the ticks to red.


```{r}

graph2+
  theme(axis.ticks.length = unit(-1, "mm"),
        axis.ticks = element_line(color = 'red'))
```
# Task 18
# In graph2:
# Change plot title's color to 'blue'.
# Change the subplot's face as italic and color to blue.
# Increase the caption's letter size and color to gray and face to bold. 


```{r}
graph2+
  theme(
    plot.title = element_text(colour = "blue"),
    plot.subtitle = element_text(face = "italic", color="blue"),
    plot.caption = element_text(size = 12, color = "gray", face = "bold")
  )
```
# Task 19
#In graph2:
# Change the plot background to "light blue".
# Remove grid lines.
# Change the panel background to "light blue".
# Change the legend background to "light blue".

```{r}

graph3<-graph2+
  theme(plot.background = element_rect(fill = "light blue"),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "light blue"),
        legend.background = element_rect(fill="light blue") )

graph3
```

#Task 20
#Label the highest price point of Onion dry in graph3 as "Highest price"

```{r}
graph3+geom_seg+geom_label(mapping = aes(x=2014, y=75, label= "Highest price"))
```
# Task 21

# Create a bbc style graph for graph2:

```{r , warning=FALSE, message=FALSE}
#)install.packages('devtools')
#devtools::install_github('bbc/bbplot')

library(bbplot)

graph4<-graph2+bbc_style()
graph4
```
# Task 22
# Save bbc_style graph using finalise_plot() function.

```{r}
finalise_plot(
  plot_name = graph4,
  save_filepath = "./data/graph4.png",
  width_pixels = 500,
  height_pixels = 500,
  source_name = "Opendata Nepal"
  
)
```

