---
title: "Simple linear regression"
author: "SanjayHamal"
date: "6/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Task1
Lets look at a simple dataset. Load the sales dataset from your data folder and save it under the name 'budget'.
```{r}
#Lets look at a simple dataset. Load the sales dataset from your data folder and save it under the name 'budget'.

library(tidyverse)
budget<- read.csv("./data/sales.csv")
budget

```


#Task2
Lets look at the relationship between advertisement budget and sales.

```{r}

ggplot(data =    ,
       mapping = aes(x=advertisement_budget, y= sales))  
  




```

#Task3
Check for outliers[univariate]
Hint : you can use box plot:geom_boxplot() to see if there are any outliers

```{r}
.


ggplot(data=budget, aes(y=sales)) + 





```

#Task4
Another method to check if there are any outliers.
```{r}


#install.packagaes(rstatix)
library(rstatix)
identify_outliers(data = budget, variable = "sales")

is_outlier(budget$sales)
is_extreme(budget$sales)
```


#Task5
Remove outliers

```{r}

budget<- budget %>% filter(is_outlier(sales)==F)
budget
```

#Task6
Again visualize your dataset for outliers using box plot.
```{r}

ggplot(data = budget, mapping= aes(y= sales))+ 

```

#Task7
Create a linear regression model to predict sales based on advertisement_budget.

```{r}

#install.packages("MASS")
library(MASS)

#Linear model for predicting values of Sales based on Advertisement_budget.

model1<- lm(sales~advertisement_budget, data=budget)


summary(model1)

```
#Task8
Regression plot

```{r}
#Graph of linear model.

ggplot(data=budget, aes(x=advertisement_budget, y= sales))+
  
  geom_point()+
  
  geom_smooth(method='lm', se=F)
```

#Task9
Predict Sales for new dataset

```{r}

#Create a new dataset
New_ad_budget<- data.frame(advertisement_budget= c(100, 1000, 10000, 100000))

New_ad_budget

predict.lm(model1, New_ad_budget)
```



