---
title: "Base R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Your Turn 01

# 1. Assign some number to num1 variable and print out.
# 2. Assign alphabet to alpha1 variable and print out.
# 3. Don't forget to write some comments.


```{r}


```


### Your Turn 02


# Find class of num1 and num2 variables

```{r}

```


### Your Turn 03

# Create a new vector called vec3

# Find the data type of vec3

```{r}







```


## Your Turn 04


```{r}
# Perform Arthmetic operations 

x <- 10
y <- 5

# Addition
x + y

# Subtraction


## Multiplication


## Division


####################################333

## Expo

5 ^ 2


99 ^ 3


```

## Your Turn 05



```{r}

x <- 5
y <- 10


## Greater than (>)

x > y

## Less than (<)


## Equals to (==)



## Not Equal to (!=)


## Greater than equal to (>=)


## Less than equal to (<=)



```

## Logical Operator

```{r}
x <- 5
y <- 10

## check if x & y is greater than 3


```


## OR Operator


```{r}
x <- 5 
y <- 10

## check if x or is greater 2



```


## NOT Operator


```{r}
x <- 5

## check if x is not greater than 3

print(!(x>3))
```

## Function


```{r}

add_me <- function(x, y) {
  
  x + y
  
}

add_me(2,5)


```



## Data Frames

## check uppper / lowest 6 data 

```{r}
head(cars)


tail(cars)
```


## create data frame

```{r}
## custom data

data <- data.frame(
  id = 1:5,
  name = c("Bikash", "Sameer", "Jiniya", "Ayusha", "Tanusha"),
  associate = c("KU", "KU", "KU", "Wiseyak", "Prime College"),
  tools_used = c("Excel", "Excel", "Excel", "SAS", "Python"),
  gender = c("Male", "Male", "Female", "Female", "Female")
)


```


```{r}
## dimensions

nrow()

ncol()

dim()

```


```{r}
## column / variable names

names()
```


```{r}
str()


```

```{r}
summary()
```

## Extract Data


```{r}
## Extract first two rows & columns

data[1:2, 1:2]

```

```{r}
## Extract second row and all columns

data[2, ]

```

```{r}
## Extract 3rd row with 2nd and 4th column

data[3, c(2, )]
```


```{r}
# Extract 2nd and 4th row with 2nd, 3rd and 4th column

data[c( ,4), c(3,4)]
```



### Your Turn 04

> Extract column: name and tools_used
> Extract row: 2nd only
> Extract row: 3rd and 4th along with columns: name, gender, tools_used


```{r}

```


## Your Turn 05

> Add "blood_group" column to the data frame


```{r}




```


## Example

```{r}
new_data <- data.frame(
  id = 6:9,
  name = c("Sanjay", "Sarun", "Abhishek", "Binod"),
  associate = c("Numeric Mind", "KU", "KU", "Numeric Mind"),
  tools_used = c("R", "SAS", "Excel", "R"),
  gender = "Male",
  address = c("Bhaktapur", "Lalitpur", NA, "Kathmandu"),
  blood_group = c("F", "G", "H", "I")
)
```

## Row bind

```{r}
updated_data <- (data, new_data)

head(updated_data)

```

## Merge

```{r}
prof_data <- data.frame(
  id = 1:9,
  phone = sample(9800000000:9863999999, 9),
  profession = "Student"
)


final_data <- (prof_data, updated_data, by = "id")


head(final_data)
```


```{r}
names(final_data)[names(final_data)=="name"] <- "first_name"
names(final_data)
```

